% You should title the file with a .tex extension (hw1.tex, for example)
\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}

\oddsidemargin0cm
\topmargin-2cm     %I recommend adding these three lines to increase the 
\textwidth16.5cm   %amount of usable space on the page (and save trees)
\textheight23.5cm  

\newcommand{\question}[2] {\vspace{.25in} \hrule\vspace{0.5em}
	\noindent{\bf #1: #2} \vspace{0.5em}
	\hrule \vspace{.10in}}
\renewcommand{\part}[1] {\vspace{.10in} {\bf (#1)}}

\newcommand{\myname}{Nishad Gothoskar}
\newcommand{\myandrew}{ngothosk}
\newcommand{\myhwnum}{2}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt plus 1pt}

\pagestyle{fancyplain}
\lhead{\fancyplain{}{\textbf{HW\myhwnum}}}      % Note the different brackets!
\rhead{\fancyplain{}{\myname\\ \myandrew}}
\chead{\fancyplain{}{Green Computing}}

\begin{document}
	
	\medskip                        % Skip a "medium" amount of space
	% (latex determines what medium is)
	% Also try: \bigskip, \littleskip
	
	\thispagestyle{plain}
	\begin{center}                  % Center the following lines
		{\Large Enhancing Mobile Apps To Use Sensor Hubs Without Programmer Effort} \\
		\myname \\
		\myandrew @andrew.cmu.edu\\
	\end{center}
	
	\question{1}{Summary}
	\quad Sensors are an important compenent in the future of technology. Heart rate sensors, GPS, accelerometer, gyroscope, etc. Their continuous sensing allows our devices to gather immense amounts of information and adapt and learn accordingly.
	
	\question{2}{Strengths}
	\begin{itemize}
		\item Testing profiling on popular apps gives us insight on how eprof works on a variety of different type
		\item I feel like integrating this into developing software like Visual Studio and XCode will make it something that developers have open all the time. Raising developer awareness about energy usage is key
	\end{itemize}
	\question{3}{Weaknesses}
	\begin{itemize}
		\item I didn't like how they dealt with asynchronous power. It just attributes it to the last entity. This might say an app is using more energy than it actually is.
		\item Maybe iOS too.
	\end{itemize}
	\question{4}{Future Directions}
	\begin{itemize}
		\item Recommendations on how to reduce energy usage
		\item A little bit of a hard to understand paper.
	\end{itemize}

\end{document}


